---
output: github_document
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/radjust)](https://cran.r-project.org/package=radjust)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

### radjust: Replicability Adjusted p-values for Two Independent Studies with Multiple Endpoints

This package provides the adjusted p-values for the null hypothesis of no replicability across studies for two study designs: a primary and follow-up study, where the features in the follow-up study are selected from the primary study; two independent studies, where the features for replicability are first selected in each study separately. The latter design is the one encountered in typical meta-analysis of two studies, but the inference is for replicability rather than for identifying the features that are nonnull in at least one study. 

#### Examples

Two independent studies:

```{r example1}

library(radjust)

## transform the example two-sided p-values to one-sided in the same direction (left):
## (we use the direction of the test statistic to do so and assume that it is continuous)
pv1 <- ifelse(mice$dir_is_left1, mice$twosided_pv1/2, 1-mice$twosided_pv1/2)
pv2 <- ifelse(mice$dir_is_left2, mice$twosided_pv2/2, 1-mice$twosided_pv2/2)

radjust_sym(pv1, pv2, input_type = "all", directional_rep_claim = TRUE, variant = "adaptive", alpha=0.025)
```

Primary and follow-up studies:

```{r example2}
rv  <- radjust_pf(pv1 = crohn$pv1, pv2 = crohn$pv1, m = 635547)
head(rv)
```

#### Installation

You can install radjust from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("shay-y/radjust")
```

